\section{Reviewer and cryptanalysis checklist}
\label{app:checklist}

Before submitting a paper or releasing software, the following questions should be answered.

\subsection{Assumptions}

\begin{enumerate}
    \item Are the exact sparse-LPN parameters stated, including sample counts from all keys and ciphertexts?
    \item Does the proof use only standard sparse-LPN/q-ary LPN assumptions, or does it introduce an additional hidden assumption?
    \item Are low-noise regimes justified against known attacks?
    \item Does any optimization introduce ring, module, cyclic, quasi-cyclic, or ideal structure that changes the assumption?
\end{enumerate}

\subsection{Correctness}

\begin{enumerate}
    \item Are empirical failure rates consistent with the theoretical bounds?
    \item Is the final row support measured rather than only upper-bounded?
    \item Does the compactor decoder succeed at the observed effective q-ary error rate?
    \item Is repetition/plurality independent across replicas?
\end{enumerate}

\subsection{Security proof}

\begin{enumerate}
    \item Are $t$, $s$, and $r$ independent?
    \item Does the expansion key encrypt $\tilde{t}$ under $s$ only, avoiding circularity?
    \item Does the compaction key encrypt $\tilde{s}$ under $r$ only, avoiding circularity?
    \item Are all hybrids efficient and simulatable?
    \item Is the total exposed sample count within the assumed hardness regime?
\end{enumerate}

\subsection{Implementation}

\begin{enumerate}
    \item Are field operations constant-time where needed?
    \item Is noise sampling unbiased?
    \item Are sparse rows stored canonically to avoid duplicate-index bugs?
    \item Are decoding failures handled without leaking side information?
    \item Are parameter files machine-readable and bound to test vectors?
\end{enumerate}
