\section{C3 Seeded Block-Dictionary Storage}
\label{app:c3-seeded}

The C2 block-dictionary compactor reduces the number of accumulated CLPN noise
terms by publishing encryptions of all nonzero block inner products
$\langle u,\tilde{s}^{(j)}\rangle$.  Its direct implementation, however, stores a
full CLPN matrix $A$ and vector $b$ for every dictionary entry.  This appendix
records a storage refinement implemented in the validation repository.

\paragraph{Seeded CLPN ciphertexts.}
For each dictionary entry, sample a public seed $\sigma$ and define
$A_\sigma\in\F_q^{m_c\times n_c}$ by a deterministic expander.  Instead of
storing $(A_\sigma,b)$, the public key stores
\[
  (\sigma,b),
  \qquad
  b=A_\sigma r + x\mathbf{1}+e,
\]
where $x=\langle u,\tilde{s}^{(j)}\rangle$ is the dictionary plaintext and $r$
is the CLPN compaction secret.  Linear homomorphic addition concatenates seeded
matrix terms and adds the corresponding $b$ vectors.  To decrypt an aggregate
ciphertext, the holder of $r$ regenerates the required rows of each
$A_\sigma$ and plurality-decodes the residual.

\paragraph{Correctness.}
Let a compacted C3 ciphertext be the linear combination
\[
  (b,\{(\alpha_t,\sigma_t)\}_{t=1}^T),
  \qquad
  b=\sum_{t=1}^T\alpha_t b_t .
\]
Then
\[
  b-\sum_{t=1}^T\alpha_t A_{\sigma_t}r
  =\left(\sum_{t=1}^T\alpha_t x_t\right)\mathbf{1}
   +\sum_{t=1}^T\alpha_t e_t .
\]
Thus the plaintext and noise law are exactly those of dense C2.  Seeded storage
changes materialization cost but not the correctness invariant.

\paragraph{Security accounting.}
The public matrices are derivable from the seeds, so C3 exposes the same q-ary
LPN sample surface as dense C2: if the dictionary contains $M_{\mathrm{dict}}$ entries,
then the public compaction surface contains $M_{\mathrm{dict}}m_c$ LPN rows.  Therefore
seeding must not be claimed as a security improvement.  It is a key-size and
memory-traffic optimization only.  The validation repository adds a dedicated
q-ary/sparse-LPN surface estimator that reports the public sample count,
sample-to-dimension ratio, no-clean-subset and Prange-style screens, and a
q-ary block-BKW scan following the classical BKW line of work
\cite{BlumKalaiWasserman2003,LevieilFouque2006,BogosEtAl2015,EsserEtAl2017LPNDecoded}.

\paragraph{Storage comparison.}
Ignoring small serialization overheads, dense C2 stores approximately
\[
  M_{\mathrm{dict}}m_c(n_c+1)
\]
field elements.  Seeded C3 stores approximately
\[
  M_{\mathrm{dict}}m_c + M_{\mathrm{dict}}\cdot\frac{\lambda_{\mathrm{seed}}}{\log_2 q}
\]
field-element equivalents, where $\lambda_{\mathrm{seed}}$ is the public seed length in
bits.  The saving is therefore close to a factor of $n_c+1$ when $m_c$ is large
relative to the seed length.  The public attack surface remains unchanged.

\paragraph{Implemented status.}
The validation package includes seeded CLPN encryption, seeded block-dictionary
key generation, end-to-end clean multiplication tests, and a seeded C3 estimator.
The implementation is still a research prototype and uses SHA-256-derived rows
for reproducibility; a production design would require a specified, reviewed,
constant-time PRG or XOF interface and independent cryptanalysis.
