\section{C4 Projective Sparse Additive-Basis Compaction}
\label{app:c4-projective}

This appendix records the C4 compaction refinement implemented in the validation repository.  The purpose of C4 is to reduce the public surface of the C2/C3 full block dictionary while preserving the small compaction-noise count that made block compaction attractive.

\subsection{Projective dictionary idea}

Let a final GSW last-row block be
\[
  \alpha = (\alpha_1,\ldots,\alpha_b) \in \F_q^b,
\]
and let the corresponding block of the extended GSW secret be
\[
  s_B = (s_1,\ldots,s_b) \in \F_q^b.
\]
A full C2 dictionary stores an encryption of
\[
  \langle \alpha,s_B\rangle
\]
for every nonzero \(\alpha\in\F_q^b\).  Hence one block requires
\[
  q^b-1
\]
public CLPN entries.

C4 observes that the linearly homomorphic compactor can scale ciphertexts.  Therefore it is unnecessary to publish separate entries for all scalar multiples of the same coefficient vector.  Let
\[
  \mathbb P^{b-1}(\F_q)
\]
denote the set of one-dimensional subspaces of \(\F_q^b\).  For each projective line, choose one representative \(u\) whose first nonzero coordinate is normalized to one.  The number of representatives is
\[
  \left|\mathbb P^{b-1}(\F_q)\right|
  = \frac{q^b-1}{q-1}.
\]
For every representative \(u\), the public C4 key stores
\[
  \Enc_{\mathrm{CLPN}}(\langle u,s_B\rangle).
\]

For any nonzero \(\alpha\in\F_q^b\), there exists a unique scalar \(\lambda\in\F_q^\ast\) and a unique normalized representative \(u\) such that
\[
  \alpha = \lambda u.
\]
The evaluator then computes
\[
  \lambda\cdot \Enc_{\mathrm{CLPN}}(\langle u,s_B\rangle),
\]
which is a CLPN encryption of
\[
  \lambda\langle u,s_B\rangle = \langle \alpha,s_B\rangle.
\]

\subsection{C4 correctness theorem}

\begin{theorem}[Projective C4 block correctness]
Let \(q\) be prime and let \(B\subseteq\{1,\ldots,N\}\) be a block of width \(b\).  Suppose the C4 public key contains CLPN encryptions of \(\langle u,s_B\rangle\) for every projective representative \(u\in\mathbb P^{b-1}(\F_q)\).  Then for every coefficient block \(\alpha\in\F_q^b\), C4 homomorphically produces a CLPN encryption of \(\langle \alpha,s_B\rangle\) using zero CLPN terms if \(\alpha=0\), and one CLPN term otherwise.
\end{theorem}

\begin{proof}
If \(\alpha=0\), the inner product is zero and the compactor contributes the zero CLPN ciphertext.  If \(\alpha\ne 0\), let \(i\) be the first index for which \(\alpha_i\ne 0\).  Set
\[
  \lambda = \alpha_i
  \quad\text{and}\quad
  u = \lambda^{-1}\alpha.
\]
Then the first nonzero coordinate of \(u\) is one, so \(u\) is exactly the projective representative stored by the public key.  By CLPN linear homomorphism,
\[
  \lambda\cdot \Enc_{\mathrm{CLPN}}(\langle u,s_B\rangle)
	ag{1}
\]
is a CLPN encryption of
\[
  \lambda\langle u,s_B\rangle
  = \langle \lambda u,s_B\rangle
  = \langle \alpha,s_B\rangle.
\]
This proves the claim.
\end{proof}

\subsection{Public-surface comparison}

For a block of width \(b\), the C4 projective dictionary has
\[
  M_{\mathrm{C4}}(b,q)=\frac{q^b-1}{q-1}
\]
entries, while C2/C3 full dictionaries have
\[
  M_{\mathrm{C2}}(b,q)=q^b-1.
\]
Thus
\[
  \frac{M_{\mathrm{C4}}}{M_{\mathrm{C2}}}=\frac{1}{q-1}.
\]
The compaction-noise term count remains one per active block, as in C2/C3.  Therefore C4 is not a storage-only transformation: it reduces both materialized key size and public CLPN sample count relative to full block dictionaries.

The cost is that C4 still publishes a structured family of related encryptions, one for every projective line in each block.  This does not by itself prove insecurity, but it is a public relation surface that must be analyzed by sparse-LPN and q-ary-LPN attack screens.

\subsection{Validation status}

The validation repository implements:
\begin{itemize}
  \item projective representatives and sparse decomposition;
  \item random additive-basis coverage screens;
  \item C4 key generation, compaction, and decryption;
  \item C4 public-surface estimates against v1, C2, and C3;
  \item end-to-end toy arithmetic-circuit tests.
\end{itemize}

The implementation should be interpreted as a research validation prototype.  The C4 construction improves the compaction-key public surface over C2/C3, but it does not remove the need for full LPN attack-cost estimation, large-sample analysis, and independent cryptanalysis.
