\section{C6 Projective-Relation Surface Estimator}
\label{app:c6-relation-surface}

C6 adds a dedicated attack-surface screen for the C4 projective compactor.
The C4 construction publishes one representative of each one-dimensional
subspace in a block.  For a block of width $b$ over $\F_q$, the number of
public representatives is
\[
    M_b = \frac{q^b-1}{q-1}.
\]
This is a factor of roughly $q$ smaller than the non-zero C2 dictionary, but
it is still a highly structured public set.

\paragraph{Projective-line relations.}
The important C6 correction is that a full projective block of width
$b\geq 2$ has many weight-three linear dependencies.  The number of
projective lines in $\mathrm{PG}(b-1,q)$ is the Gaussian binomial coefficient
\[
    {b \brack 2}_q
    =
    \frac{(q^b-1)(q^{b-1}-1)}{(q^2-1)(q-1)}.
\]
Every projective line has $q+1$ points, and every triple of distinct points
on that line is linearly dependent.  Thus the raw number of weight-three
projective-line relations in one block is
\[
    R_{3,b}
    =
    {b \brack 2}_q {q+1 \choose 3}.
\]
For $b=1$ this number is zero; for every $b\geq 2$ it is positive.  This
replaces the earlier rough C5 heuristic that treated the generic minimum
relation weight as $b+1$.  The generic statement is true for arbitrary
vectors in general position, but the complete projective set is not in
general position: it contains complete projective lines.

\paragraph{Known-zero CLPN combinations.}
Let the C4 key contain CLPN ciphertexts of
$\langle u_j,s_B\rangle$ for public block masks $u_j$.  If
\[
    a u_i + b u_j + c u_k = 0
\]
for non-zero $a,b,c\in\F_q$, then the same linear combination of the three
CLPN ciphertexts encrypts the known message zero.  The resulting row-level
samples have q-ary symmetric noise rate
\[
    \eta_3
    =
    \frac{q-1}{q}
    \left(1-
    \left(1-\frac{q\eta_c}{q-1}\right)^3
    \right),
\]
by the q-ary piling-up formula.  These relation-derived samples must be
screened separately from ordinary row differences inside a single CLPN
ciphertext, which have effective noise $\eta_2$.

\paragraph{Raw count versus rank-capped count.}
The raw number $R_{3,b}$ should not be interpreted as an independence count.
The space of all linear relations among the $M_b$ public projective
representatives has dimension
\[
    K_b = M_b-b.
\]
Therefore the C6 estimator reports both
\[
    m_c \sum_B R_{3,b_B}
\]
as a raw low-weight relation surface and
\[
    m_c \sum_B K_{b_B}
\]
as a rank-capped independence proxy.  Both quantities matter: the raw count
measures the adversary's search surface, while the rank-capped count prevents
the screen from pretending that all low-weight relations are independent.

\paragraph{C6 diagnostic verdict.}
The C6 validation package screens four surfaces:
\begin{enumerate}
    \item sparse-LPN expansion-key rows;
    \item C4 CLPN row-difference samples;
    \item C4 weight-three relation samples with rank-capped counting;
    \item C4 weight-three relation samples with raw upper-bound counting.
\end{enumerate}
The current C6 result rejects full projective C4 as the main security
candidate for block width at least two.  This is not a correctness failure;
it is a public-surface warning.  The algebraic compactor works, but abundant
weight-three public relations give an attacker known-zero q-ary-LPN-style
samples at low accumulated noise.  This interacts directly with the known
importance of BKW-style algorithms and information-set-decoding attacks for
LPN and code-based cryptography \cite{BlumKalaiWasserman2003,BogosEtAl2015,Prange1962,Stern1989,MayMeurerThomae2011,BeckerJouxMayMeurer2012}.

\paragraph{Implication for the next construction.}
C7 should replace the full projective dictionary with a relation-resistant
compaction layer.  Possible directions are incomplete randomized additive
bases with screened sparse-kernel weight, salted block masks that prevent
public cancellation to known-zero messages, or a decoding-based compactor
whose public generator has no abundant low-weight kernel.  The target
property is no longer only coverage; the public basis must also have high
minimum sparse-kernel weight while maintaining compaction noise low enough for
correctness.
